---
title: "BiocVersion: Identify Bioconductor Version"
author:
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
- name: Marcel Ramos
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
date: "`r BiocStyle::doc_date()`"
vignette: |
  %\VignetteIndexEntry{BiocVersion}
  %\VignetteEngine{knitr::markdown}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    toc_float: true
Package: BiocVersion
---

# Introduction

This package provides a way to obtain the ground-truth Bioconductor version
because it lives in the repository that it versions. When a new version is
released, the Bioconductor version is reflected in the packages `DESCRIPTION`
file.

# Installation

```{r,eval=FALSE}
if (!require("BiocManager", quietly = TRUE)
    install.packages("BiocManager")

BiocManager::install("BiocVersion")
```

# Load packages

```{r,include=TRUE,results="hide",message=FALSE,warning=FALSE}
library(BiocManager)
library(BiocVersion)
```

# Bioconductor Version

To obtain the Bioconductor version, `BiocManager` employs a method such
as:

```{r}
ver <- packageVersion("BiocVersion")
package_version(ver[, 1:2])
```

```{r}
version()
```

# Session Information

```{r}
sessionInfo()
```
